\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{listings} % Required for displaying code

\title{Project 2}
\date{May 5 2023}

\begin{document}

\maketitle
\noindent We have {\bf read and understood the assignment instructions}. We certify that the submitted work does not violate any academic misconduct rules, and that it is solely our own work. By listing our names below we acknowledge that any misconduct will result in appropriate consequences. 

\vspace{0.2in}

\noindent {\em ``As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do.
Accountable together -- we are Purdue.''}

\vspace{0.3in}

\begin{table}[h!]
  \begin{center}
    \label{tab:table1}
    \begin{tabular}{c|ccccc|c|c}
      Student & Q1 & Q2 & Q3 & Q4 & Q5 & Overall & DIFF\\
      \hline
      Chirayu Marwaha & 20 & 20 & 20 & 20 & 20 & 100 & 0\\
      Liz Parmenter & 20 & 20 & 20 & 20 & 20 & 100 & 0\\
      Abdulla Almarzooqi & 20 & 20 & 20 & 20 & 20 & 100 & 0\\
      Hongyi Shen & 20 & 20 & 20 & 20 & 20 & 100 & 0\\
      Kevin Braner & 20 & 20 & 20 & 20 & 20 & 100 & 0\\
      \hline
      St Dev & 0 & 0 & 0 & 0 & 0 & 0 & 0
    \end{tabular}
  \end{center}
\end{table}

\section{Introduction}
Help the reader understand why someone should care about or be interested in the activities done in this project. You should also elaborate on the goals of the project without quoting the direct text from the assignment document.

\section{Methods}
Here, please discuss your approach to completing the project activities and data analysis. Elaborate on strategic decisions made within the design processes and justify why those decisions were best for the respective goals. Include which user evaluation criteria you researched were important factors/information and assumptions made with each section.

\section{Results}
Here, we represent the final product of the decisions explained in the Methods Section. In this section, be sure to include sufficient detail on the inner working of the code. Ideally with a simple diagram. It should be made clear to the reader how the results were obtained. You can include pseudocode but limit it.

\section{Conclusion}
Summarize all sections of the report and give a concise summary of the key elements you discussed.


\section{References}
APA style


\section{Appendix}
\subsection{Appendix A: Testing/Correctness/Verification}
\subsection{Appendix B:Run-time Complexity and Wall-time}
\subsection{Appendix C: Performance}
\subsection{Appendix D: Justification}





\end{document}
